The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2015-01-15 paper/mri_paper.tex
missing f
description of cells with Pm
run correct Pm 1E-4 with 512 grid

\beq
\mathbf{J} = \frac{2}{\beta}\nabla\times\mathbf{B}.
\eeq

@@

The role of the boundary layers changes with Pm. As Pm decreases, the width of the boundary layer becomes increasingly narrow (Figure \ref{u_secondorder_by_Pm}). The geometry of the velocity in the $x-z$ plane begins as a series of MRI ``cells" whose structure is radially narrow in the bulk of the flow. These central cells then stretch and grow, until at $Pm \sim 10^{-5}$ the bulk cells dominate the flow. The relative importance of the $u_y$ second order perturbation to the first order perturbation increases as well (CHECK, PLOT).

@@

\beq\label{ampeq2_hmri}
\partial_T \beta = - m \partial_Z^2 \beta + \frac{1}{\reym} \partial_Z^2 \beta \, - \, s \xi 2 \left|\alpha\right|\partial_Z \alpha \, - \, \xi\partial_Z^2 \beta,
\eeq

>>>>

\beq
%\mathbf{J} = \frac{2}{\beta}\nabla\times\mathbf{B}.
\mathbf{J} = \nabla\times\mathbf{B},.
\eeq

in units where the permittivity of free space is unity.

@@

The role of the boundary layers changes with Pm. As Pm decreases, the width of the boundary layer becomes increasingly narrow (Figure \ref{u_secondorder_by_Pm}). The geometry of the velocity in the $x-z$ plane begins as a series of MRI ``cells" whose structure is radially narrow in the bulk of the flow. As Pm is decreased, the saturation geometry of the central cells stretches radially, until at Pm $\sim 10^{-5}$ the bulk cells dominate the flow. The relative importance of the $u_y$ second order perturbation to the first order perturbation increases as well (CHECK, PLOT).

@@

\beq\label{ampeq2_hmri}
\partial_T \beta = - m \partial_Z^2 \beta + \frac{1}{\reym} \partial_Z^2 \beta \, - \, s \xi 2 \left|\alpha\right|\partial_Z \alpha \, - \, f\xi\partial_Z^2 \beta,
\eeq
